week getbackontrack

### 2024-11-11 weekbacktrack.Rmd
weekbacktrackupdate111124

+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------------------+

@@

+:==============================================================================================+:===========================================================+:==============================================================+:===========================================================================================+:================================================================+:==========================================================================+:====================================================================+

@@

| ![](images/used_arson%20frog.jpg)                                                             | ![](images/used_arson%20frog.jpg){width="952"}             | ![](images/socialnetworking.jpg){width="800"}Clarify RQs [D]\ | ![](images/socialnetworking_meh.jpg){width="800"}Rework schedule [according Jochems input] | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/timetopanic.gif){width="800"}[chores at home, depression day]  | ![](images/socialnetworking_meh.jpg)Get polSci data,                |

@@

| ![](images/socialnetworking_meh.jpg){width="800"}\                                            | ![](images/used_arson%20frog.jpg){width="952"}[work]       | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking_meh.jpg){width="800"}\                                         | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/socialnetworking.jpg){width="800"}rewrite intro and Theory [W] | ![](images/timetopanic.gif){width="800"}[Grandmas bday celebration] |

@@

|                                                                                               | Talk to Jochem                                             |                                                               |                                                                                            |                                                                 | read into specifying model [S4]                                           |                                                                     |
| Define variables (get stuck with sienaDependent)                                              |                                                            |                                                               | & create effects structure [S2]                                                            | journal, make submenus                                          |                                                                           |                                                                     |

@@

| check in with Jochem                                                                          |                                                            |                                                               | make h index                                                                               | Reorganize code                                                 |                                                                           |                                                                     |

@@

| ![](images/socialnetworking_meh.jpg){width="800"}Write Data & methods part [W]                | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking.jpg){width="800"}Data & methods part [W]\                      | ![](images/socialnetworking.jpg){width="800"}estimate model     | ![](images/socialnetworking.jpg){width="800"}goodness of fit [S6]         | ![](images/kermit-panic.gif)                                        |

@@

| Check in with Jochem                                                                          |                                                            |                                                               |                                                                                            | goodness of fit                                                 | Start Results [W]                                                         | [chores at home and university]                                     |
+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------------------+

@@

| ![](images/used_arson%20frog.jpg)[Research project course starts: little time to work on SNA] | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking_meh.jpg){width="800"}Results [W]                               | ![](images/socialnetworking.jpg){width="800"}Finish Results [W] | ![](images/socialnetworking.jpg){width="800"}Discussion & conclusion [W]  |                                                                     |

@@

| Check in with Jochem?                                                                         |                                                            |                                                               |                                                                                            | Discussion & conclusion [W]                                     | ![](images/kermit-panic.gif){width="500"}Format project website& hand in! |                                                                     |
+-----------------------------------------------------------------------------------------------+------------------------------------------------------------+---------------------------------------------------------------+--------------------------------------------------------------------------------------------+-----------------------------------------------------------------+---------------------------------------------------------------------------+---------------------------------------------------------------------+

>>>>

+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------+

@@

+:==================================================================================================+:=============================================================+:================================================================+:===========================================================================================+:==============================================================================+:===========================================================================+:=========================================================================+
| 28\.                                                                                              | 29\.                                                         | 30\.                                                            | 31\.                                                                                       | **01.11.**                                                                    | 02\.                                                                       | 03\.                                                                     |

@@

| ![](images/used_arson%20frog.jpg)                                                                 | ![](images/used_arson%20frog.jpg){width="952"}               | ![](images/socialnetworking.jpg){width="800"}Clarify RQs [D]\   | ![](images/socialnetworking_meh.jpg){width="800"}Rework schedule [according Jochems input] | ![](images/socialnetworking.jpg){width="800"}\                                | ![](images/timetopanic.gif){width="800"}*[chores at home, depression day]* | ![](images/socialnetworking_meh.jpg)Get polSci data,                     |

@@

| ![](images/socialnetworking_meh.jpg){width="800"}\                                                | ![](images/used_arson%20frog.jpg){width="952"}*[work]*       | ![](images/used_arson%20frog.jpg)*[university]*                 | ![](images/socialnetworking_meh.jpg){width="800"}\                                         | ![](images/socialnetworking.jpg){width="800"}\                                | ![](images/kermit-panic.gif){width="800"}*[personal circumstances]*        | ![](images/timetopanic.gif){width="800"}*[Grandmas bday celebration]*    |

@@

|                                                                                                   | Talk to Jochem                                               |                                                                 |                                                                                            |                                                                               |                                                                            |                                                                          |
| Define variables (get stuck with sienaDependent)                                                  |                                                              |                                                                 | make h index                                                                               | journal, make submenus                                                        |                                                                            |                                                                          |

@@

| check in with Jochem                                                                              |                                                              |                                                                 |                                                                                            | Restructure code                                                              |                                                                            |                                                                          |

@@

| ![](images/socialnetworking_meh.jpg){width="800"}Check in with Jochem                             | ![](images/used_arson%20frog.jpg){width="952"}*[university]* | ![](images/used_arson%20frog.jpg)*[university]*                 | ![](images/socialnetworking.jpg){width="800"}Continue description & plotting [S3]          | ![](images/socialnetworking.jpg){width="800"}Write theory [W]                 | ![](images/socialnetworking.jpg){width="800"}goodness of fit [S6]          | ![](images/timetopanic.gif)*[chores at home and university]*             |

@@

| Continue description & plotting [S3]                                                              |                                                              |                                                                 | Data & methods part [W]                                                                    | estimate model [S5]                                                           | Start Results [W]                                                          |                                                                          |
|                                                                                                   |                                                              |                                                                 | Write introduction and theory [W]                                                          | goodness of fit [S6]                                                          |                                                                            |                                                                          |
+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------+

@@

| ![](images/socialnetworking_meh.jpg){width="800"}*[RP course starts: little time to work on SNA]* | ![](images/used_arson%20frog.jpg){width="952"}*[university]* | ![](images/used_arson%20frog.jpg)*[university]*                 | ![](images/socialnetworking_meh.jpg){width="800"}*[LOW capacities]*                        | ![](images/socialnetworking_meh.jpg)*[LOW capacities]*                        | ![](images/socialnetworking.jpg){width="800"}Discussion & conclusion [W]   | ![](images/socialnetworking_meh.jpg)*[chores at home, mental breakdown]* |

@@

| Check in with Jochem                                                                              |                                                              |                                                                 | Results [W]                                                                                | Finish Results [W]                                                            |                                                                            | Rework intro [W]                                                         |
+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------+
| 25\.                                                                                              | 26\.                                                         | 27\.                                                            | 28\.                                                                                       | 29\.                                                                          | 30\.                                                                       | **1.12.**                                                                |
| ![](images/socialnetworking.jpg){width="800"}Discussion & conclusion [W]                          | ![](images/used_arson frog.jpg)*[university]*                | ![](images/socialnetworking_meh.jpg){width="800"}*[university]* | ![](images/socialnetworking_meh.jpg){width="800"}[*work, bc I don't want to get fired]*    | ![](images/socialnetworking_meh.jpg)*[university]*                            | *[Catch up on uni]*                                                        | *[Catch up on uni]*                                                      |
|                                                                                                   |                                                              | Discussion & conclusion [W]                                     | Finish discussion & conclusion [W]                                                         | ![](images/kermit-panic.gif){width="800"}**Format project website& hand in!** |                                                                            |                                                                          |
+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------+
